---
title: "Rising Stars Muay Thai: Data-Driven Insights & Strategic Roadmap"
author: "Juan De La Cruz"
format:
  revealjs:
    transition: fade
    slide-number: true
    toc: false
    incremental: true
    embed-resources: true
---

## Project Overview

**Data-Driven Growth Strategy for Rising Stars Muay Thai**

-   Improve marketing performance and conversions\
-   Build analytics infrastructure\
-   Enable data-driven decision-making

------------------------------------------------------------------------

## Data & Sources

-   **Google Analytics 4 (Website):** User behavior, traffic, engagement\
-   **Eventbrite:** Ticket sales and attendance\
-   **Social Media:** Instagram & Facebook insights\
-   **Customer Data:** Demographics and behavior\
-   **Influencer Data:** Fighter engagement performance

------------------------------------------------------------------------

## Managerial Problems

-   No centralized website\
-   No analytics or tracking system\
-   No ability to measure ROI\
-   Limited customer insights\
-   Low membership conversion\
-   No influencer performance tracking

------------------------------------------------------------------------

## Digital Transformation

::: callout-important
A fully functional website was developed and deployed using GitHub Pages.
:::

-   Google Analytics 4 integrated\
-   Real-time tracking implemented\
-   Website Traffic Analytics page created\
-   Data infrastructure established

------------------------------------------------------------------------

## Target Audience

-   Founder / Owner\
-   Marketing Team\
-   Event Operations Managers\
-   Sponsors and Partners

------------------------------------------------------------------------

## Research Questions

-   How can a website improve engagement and sales?\
-   What audience segments are most valuable?\
-   What content drives conversions?\
-   Where do users drop off?\
-   How do events impact memberships?\
-   Which fighters generate the highest ROI?

------------------------------------------------------------------------

## Methods Used

-   Descriptive Analytics\
-   Cluster Analysis\
-   Customer Journey Analysis\
-   Conversion Rate Analysis\
-   Logistic Regression\
-   A/B Testing\
-   Cross-Tabulation

------------------------------------------------------------------------

## Website Analytics Implementation

::: callout-tip
Google Analytics 4 is actively tracking user behavior on the website.
:::

-   Tracks users, sessions, and page views\
-   Identifies high-performing content\
-   Measures engagement and interaction

------------------------------------------------------------------------

## Traffic Forecast

-   Website is newly launched → limited real data\
-   Created a **6-month forecast model**

Growth driven by: - Resume & LinkedIn sharing\
- Networking exposure\
- Repeat visitors

------------------------------------------------------------------------

## Traffic Forecast Visualization

```{r}
months <- c("Month 1", "Month 2", "Month 3", "Month 4", "Month 5", "Month 6")
users <- c(25, 55, 90, 135, 185, 245)

plot(
  users,
  type = "b",
  pch = 19,
  xaxt = "n",
  xlab = "Month",
  ylab = "Projected Users",
  main = "Projected Website Traffic Growth"
)

axis(1, at = 1:6, labels = months)
grid()
```

------------------------------------------------------------------------

## Multi-Metric Forecast

```{r}
users <- c(25, 55, 90, 135, 185, 245)
sessions <- c(35, 75, 125, 180, 245, 320)
pageviews <- c(80, 170, 290, 430, 600, 780)

plot(users, type="o", xaxt="n", ylab="Count", xlab="Month",
     main="Projected Growth (Users, Sessions, Page Views)")

lines(sessions, type="o", lty=2)
lines(pageviews, type="o", lty=3)

axis(1, at=1:6, labels=c("M1","M2","M3","M4","M5","M6"))

legend("topleft",
       legend=c("Users","Sessions","Page Views"),
       lty=c(1,2,3))
```

------------------------------------------------------------------------

## Business Impact

-   Increased ticket sales\
-   Higher membership conversions\
-   Improved marketing ROI\
-   Better audience targeting\
-   Data-driven decision-making\
-   Stronger sponsorship positioning

------------------------------------------------------------------------

## Conclusion

-   Website + GA4 = analytics foundation\
-   Forecasting enables proactive strategy\
-   Transition from intuition → data-driven growth
