---
title: "website-traffic-analytics"
---

# Overview 

This website uses Google Analytics 4 to track visitor behavior and engagement. The purpose of this page is to summarize how website traffic will be measured and to forecast expected growth over time.\
\
Because this portfolio website was recently published, there is currently limited historical data available. Google Analytics will continue collecting real visitor data as the website is shared through resumes, LinkedIn, job applications, and professional networking.

# Google Analytics Tracking 

Google Analytics 4 has been successfully integrated into this website using the following measurement ID:\
\
\*\*G-NZ6JF0QEKB\*\*\
\
This implementation allows the website to collect real-time data on user activity and engagement. The tracking is active across all pages of the portfolio, enabling analysis of how visitors navigate and interact with the content.\
\
Google Analytics will be used to monitor performance and identify which sections of the website generate the most interest.

# Key Metrics 

The following key performance indicators (KPIs) are tracked using Google Analytics:

<div>

## Users

The number of unique visitors to the website. This helps measure overall reach.

</div>

<div>

## Sessions 

The total number of visits to the website. A single user can have multiple sessions.

</div>

<div>

## Page Views 

The total number of pages viewed across all sessions. This indicates which content is most popular.

</div>

<div>

## Engagement Rate

The percentage of sessions where users actively interact with the website (such as clicking links or viewing multiple pages).

</div>

<div>

## Top Pages

Identifies which pages receive the highest traffic, helping determine which projects or sections attract the most attention.

</div>

# Current Tracking Status

Since the website was recently launched, real-time data is still being collected. Google Analytics tracking is active, and user activity will continue to populate as visitors access the site.

::: callout-important
### Status Update

Google Analytics tracking is currently active across the website. Data collection has begun and will increase as the site is shared.
:::

```{r}
current_status <- data.frame(
  Metric = c("Users", "Sessions", "Page Views", "Engagement Rate"),
  Status = c("Tracking Active", "Tracking Active", "Tracking Active", "Tracking Active")
)

knitr::kable(current_status)
```

# Six-Month Website Traffic Forecast

Since the website is newly launched and historical data is limited, a projected traffic forecast was created to estimate expected growth over the next six months.

::: callout-tip
## Forecast Purpose

This forecast provides an estimate of how website traffic may grow as the portfolio is shared through professional channels such as LinkedIn, resumes, and networking opportunities.
:::

```{r}
months <- c("Month 1", "Month 2", "Month 3", "Month 4", "Month 5", "Month 6")

projected_users <- c(25, 55, 90, 135, 185, 245)
projected_sessions <- c(35, 75, 125, 180, 245, 320)
projected_pageviews <- c(80, 170, 290, 430, 600, 780)

forecast <- data.frame(
  Month = months,
  Projected_Users = projected_users,
  Projected_Sessions = projected_sessions,
  Projected_Pageviews = projected_pageviews
)

knitr::kable(forecast)
```

# Projected Website Traffic Growth

```{r}
plot(
  projected_users,
  type = "o",
  xaxt = "n",
  xlab = "Month",
  ylab = "Projected Users",
  main = "Projected Website Traffic Growth"
)

axis(1, at = 1:6, labels = months)
grid()
```

# Forecast Interpretation

The projected data illustrates a steady increase in website traffic over the next six months. During the first month, traffic is expected to be relatively low due to the website’s recent launch and limited exposure.

As the website is shared through LinkedIn, resumes, and professional networking, traffic is expected to grow significantly. The increase in users, sessions, and page views reflects greater visibility and interest in the portfolio content.

The most noticeable growth occurs between months three and six, where traffic is projected to accelerate. This growth is driven by continued sharing, repeat visitors, and increased engagement with project pages.

Overall, the forecast suggests that the website will experience consistent growth as it becomes part of a broader professional branding and job search strategy.

# Forecast Assumptions

The projected traffic forecast is based on several key assumptions about how the website will be used and shared:

-   The website will be included on resumes and job applications.
-   The website will be shared on LinkedIn and professional platforms.
-   Recruiters and hiring managers may visit the site.
-   Visitors may explore multiple pages, increasing engagement.
-   Traffic will gradually increase over time as visibility improves.

# Conclusion

Google Analytics provides a valuable tool for measuring the effectiveness of this portfolio website. By tracking user behavior and analyzing key performance metrics, it is possible to better understand how visitors interact with the content.

Although the website is newly launched and real-time data is still being collected, the traffic forecast provides a realistic expectation of future growth. As more users visit the site, these insights can be used to optimize content, improve user experience, and enhance overall engagement.

This combination of real-time analytics and forecasting demonstrates the application of data-driven decision-making in a digital marketing context.
